Cloud Supercomputing

### 2019-04-16 writing/paper/paper.tex
Rewrite introduction.

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}

Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).

In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
To include viscosity\todo{MB: viscosity ist unmotiviert ist.
  Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}

We utilize the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.

We make the following contributions\todo{Feedback von MB: Besser hervorheben, warum diese Sachen interessant/neu sind.
Dumbser macht in seinen NS-DG papern keine komplexen Source terme, keine hydrostatic flows, etc.
}:
\begin{itemize}%
\item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
\item We use this to provide an implementation of the compressible Navier-Stokes equations.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.
\end{itemize}

@@

Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
\end{equation}
i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term.
The momentum equation is dominated by the background flow in this case.
This can lead to numerical instabilities.
To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
Note that a smilar splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
\todo{Mention differences in splitting methods}
\section{Numerics}

>>>>

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
The accurate simulation of fluid dynamics is crucial for detailed weather prediction.
\todo{Most results here are quite old.}
Because these dynamics are approximated well with the compressible Navier-Stokes equations, this is the equation set of our choice.
There are some examples, where higher order methods have been used for the simulation of clouds, such as~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
Even though these methods use a discretization with a (theoretical) unlimited space-order, they use either Runge-Kutta time integrators or semi-implicit methods.
It is well known that Runge-Kutta methods become more ineffecient for very high orders.
Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead.

We thus follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows.
\todo{LK: Heißt das hydrostatic?}
%\todo{MB: viscosity ist unmotiviert ist.
 % Lieber noch so 10--15 Zeilen drüber schreiben.}
Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.
For high-order \dg{} methods, viscosity not only models the physical reality of the problem but also helps us by smoothing out oscillations and discontinuities, thus stabilizing the simulation.
To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous}.
This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
In contrast to this paper, we focus on the simulation of complex flows with a gravitational source term and a realistic background atmosphere.
%\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}

%Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).

We base our work on the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.

We make the following contributions\todo{Feedback von MB: Besser hervorheben, warum diese Sachen interessant/neu sind.
Dumbser macht in seinen NS-DG papern keine komplexen Source terme, keine hydrostatic flows, etc.
}:
\begin{itemize}%
\item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
\item We use this to provide an implementation of the compressible Navier-Stokes equation.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.
\end{itemize}

@@

Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
\end{equation}
i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term.
The momentum equation is dominated by the background flow in this case.
Because this can lead to numerical instabilities, problems of this kind are challenging and require some care.
To lessen the impact of this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
Note that a similar and more complex splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
\todo{Mention differences in splitting methods}
\section{Numerics}
